---
title: "Discrete Probability"
author: "Rob van Laaroven"
date: "3-3-2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Monte Carlo simulations

Monte Carlo simulations model the probability of different outcomes by repeating a random process a large enough number of times that the results are similar to what would be observed if the process were repeated forever.

The sample() function draws random outcomes from a set of options.

The replicate() function repeats lines of code a set number of times. It is used with sample() and similar functions to run Monte Carlo simulations.

```{r beads}
beads <- rep(c("red", "blue"), times = c(2,3))    # create an urn with 2 red, 3 blue
beads    # view beads object
sample(beads, 1)    # sample 1 bead at random
```

## Experiment

Use replicate to do a large number of draws

```{r beads-draw-replicate}
B <- 1000000    # number of times to draw 1 bead
events <- replicate(B, sample(beads, 1))    # draw 1 bead, B times
tab <- table(events)    # make a table of outcome counts
tab    # view count table
prop.table(tab)    # view table of outcome proportions
```


You can use sample funtion to pick more than one element

```{r-sample}
sample(beads,2)
sample(beads,2)
sample(beads,2)
sample(beads,6)
```

6 Gives an error because there are only 5 beads. Default is replace=FALSE. Use replace=TRUE to simulate pick with replace. 
Note : this is much faster than replicate
```{r beads-draw-sample}
events <- sample(beads,replace = TRUE,B)  
tab<-table(events)
tab    # view count table
prop.table(tab)    # view table of outcome proportions
```

